---
title: "p8105_hw5_hw2850"
author: "Haoyang Wang"
date: "2022-11-06"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r} 
library(tidyverse)

```

#Problem 2
```{r}
homicide_raw = read_csv("data/homicide-data.csv") %>% 
  janitor::clean_names()
```
The raw data contains the homicides victims' information including the reported
date, victims' names, victims' age, victims' race, victims' sex, the cities and
the states that homicides occurred, the precise location of homicides (latitude,
longitude), and the disposition/result of homicides. 

```{r}
homicide_city_state = read_csv("data/homicide-data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(.data = ., city_state = str_c(city, ", " ,state)) %>% 
  select(-city, -state) %>% 
  mutate(
    disposition = if_else(disposition %in% c("Closed without arrest", "Open/No arrest"), "unsolved homicides", "homicides")
  )
```
Group "Closed without arrest" and "Open/No arrest" into category "unsolved homicides". Group "Closed by arrest" into category "homicides".


